Ore Polynomials in Sage

### 2013-06-14 paper/main.tex
minor changes in doc.
for the paper, Makefile and main.tex changed to proper loading of package.

\begin{sageexample}
  sage: load("ore_algebra.py", "guessing.py", "ore_operator.py");  #### TO BE FIXED ####
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: L1,L2 = A.random_element(3),A.random_element(2)    
  sage: L1.gcrd(L2, prs=__primitivePRS__)
  sage: L1.gcrd(L2, prs=__classicPRS__)
\end{sageexample}

>>>>

\begin{sageexample}
  sage: #load("ore_algebra.py", "guessing.py", "ore_operator.py");  #### TO BE FIXED ####
  sage: from ore_algebra import *
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\begin{sageexample}
  sage: A = OreAlgebra(ZZ['n'], 'Sn');                                           
  sage: L1,L2 = A.random_element(3),A.random_element(2)    
  sage: #L1.gcrd(L2, prs=__primitivePRS__)
  sage: #L1.gcrd(L2, prs=__classicPRS__)
\end{sageexample}
